\textbf{Bachelor thesis}\\ Exploration of the influence of graph parameters on the generalization error of Graph Neural Networks

### 2025-01-14 thesis/main.tex
Add thesis tex files
Update the thesis

\title{\textbf{Proposal for bachelor thesis}\\
Exploration of the influence of graph parameters on the generalization error of Graph Neural Networks}

@@

\section{Introduction}\label{sec:intro}

Graph learning became a hot topic in the field of machine learning in recent years. Graph Neural Networks (GNNs), also known as deep learning on graphs, are a class of neural networks that can operate on graph-structured data, such as social networks~\cite{easley2010networks}, biological networks~\cite{barabasi2004network}, and images~\cite{simonovsky2017dynamic}. GNNs use the structure of a graph to perform "message passing", allowing information to propagate across nodes and edges. The key idea is to iteratively aggregate and update node features by exchanging information with local neighboring nodes, which allows GNNs to capture the structural information of the graph. This information is then used to make predictions. GNNs have been demonstrated to be effective in a wide range of tasks, such as node classification~\cite{hamilton2017inductive}, edge prediction~\cite{morselli2021network}, and graph classification~\cite{gilmer2017neural}. Popular GNNs in recent years include Graph Convolutional Networks (GCN)~\cite{kipf2016semi}, Graph Attention Networks (GAT)~\cite{velickovic2020pointer}, and Message Passing Neural Networks (MPNN)~\cite{gilmer2017neural}.

@@

Before we untangle this problem, we need to define some terms with regard to the graph. In graph theory, we assume that $G=(V,E)$ is an undirected graph, where $V$ is the set of nodes and $E  \subseteq \{\{v,w\}\mid v,w \in V , v \neq w\}$ is the set of edges. We use $\mathbb{G}$ to represent the set of all possible graphs. The neighborhood of a node $v$ is denoted as $N(v)$, defined as $N(v) = \{w \mid \{v,w\} \in E\}$. The degree of a node $v$, denoted as $d(v)$, is the number of neighbors of $v$, that is, $d(v) = |N(v)|$. In addition to the nodes and edges that comprise the graph, we can attach a more complex set of data to each node.  A feature vector $x_n\in \mathbb{R}^k$, is attached to a node $v_n$, and in some cases, edge feature vectors are also included. These vectors can be used to characterize graphs or nodes in graphs. The adjacency matrix $A \in \mathbb{R}^{|V| \times |V|}$ is a matrix that represents the connections between nodes in the graph. The element $a_{ij}$ of the adjacency matrix is 1 if there is an edge between node $v_i$ and node $v_j$, and 0 otherwise.

With these foundational terms in place, we can now introduce the concept of a graph parameter. A graph parameter is a function $f: \mathbb{G} \rightarrow \mathbb{R}^d$ for $d\in \mathbb{N} >0$, which maps a graph to a d-dimensional vector over the reals. Furthermore, such functions need to be permutation invariant, i.e., $f(G) = f(\pi(G))$ for any permutation $\pi$ of the nodes of $G$, where a permutation is a function $\pi: V \rightarrow V$ and $\pi(G)$ denotes the graph obtained by permuting the nodes of $G$ according to $\pi$. A graph parameter allows us to quantify certain properties of a graph, from the basic structural numbers (number of nodes, number of edges, average degree, etc.) to distance properties (average shortest path length, diameter, etc.) to more complex properties (graph clustering coefficient, average number of coloring in the 1-WL algorithm, etc.). This thesis will focus on seven graph parameters, with definitions provided in section~\ref{sec:graph_parameters}.

Additionally, the graph classification task aims to classify a graph into one of several classes. This thesis will specifically focus on addressing this task. A key concept in evaluating model performance or generalization ability in such task is the empirical generalization error $E_{gen}$. This is a measure of how well the model generalizes to unseen data, which can be calculated as the difference between the training accuracy and the test accuracy. It is defined as

@@

The empirical generalization error is also known as the generalization gap~\cite{goodfellow2016deep}. Typically, the learning on the training dataset and test dataset behaves differently. The model may perform well on the training dataset but poorly on the test dataset. By observing the generalization error, we can decide on a stopping criterion for the training process. And the generalization error can be used to determine whether the model is overfitting or underfitting. Furthermore, the generalization error can be influenced by many factors, such as the model architecture, the hyperparameters, and the dataset. In this thesis, I will investigate how the graph parameters influence the generalization error of GNNs. The understanding of the influence of graph parameters on the generalization error of GNNs can help us to understand the behavior of GNNs so that researchers can tune GNNs to improve their predictive performance on new graphs.

\section{Experimental Setup}
The following section outlines the planned methods and materials to be employed in the experiment, including the training framework, the datasets, the models, and the graph parameters.

\subsection{Training Framework}
The training framework is based on PyTorch Geometric~\cite{fey2019fast}. PyTorch Geometric is a library for deep learning on graphs and other irregular structures. It consists of various methods and utilities to ease the implementation of GNNs.

\subsection{Datasets}
The dataset used for the classification is TUDataset~\cite{morris2020tudataset}. TUDataset is often used for the GNN evaluation. It consists of data from different domains, including small molecules, bioinformatics, social networks and synthetic. Since the size of some datasets is quite small (less than 500 data points/graphs), I will use 10-fold cross validation in the training process, in order to fully utilize the data. A dataset is split into 1:1:8, where one of the folds is treated as the test dataset and another is treated as the validation dataset. The remaining folds are used for training. The training is repeated 10 times, each time with a different test fold. The average of the generalization error over the 10 runs is calculated as the final generalization error of the model.

\subsection{Models}
In the experiment, I plan to use different GNN layers in the model, including Graph Convolutional Networks(GCN)~\cite{kipf2016semi}, Graph Attention Networks(GAT)~\cite{velickovic2020pointer}, Graph Attention Networks(GATv2)~\cite{brody2021attentive}, Simplified Graph Convolution(SGC)~\cite{wu2019simplifying}, and Message Passing Neural Networks(MPNN)~\cite{gilmer2017neural}. The GCN model is shown in the appendix. The GCN model consists of four GCN layers, each followed by a ReLU activation function. The output of the last GCN layer is passed through a global mean pooling layer, followed by two fully connected layers.

\subsection{Experimental details}
The Adam optimizer~\cite{kingma2014adam} is considered to be employed in the model. To prevent overfitting and to optimize the use of time, the early stopping is employed. The loss function is defined as the cross-entropy loss function. The hyperparameters of the model are considered to be tuned. The hyperparameters include the learning rate, batch size, hidden dimension, number of epochs, and patience in early stopping. The generalization error is calculated as the difference between the training accuracy and the test accuracy.

\subsection{Graph Parameters Under Investigation} \label{sec:graph_parameters}
As graph parameters defined abstractly in the section~\ref{sec:intro}, I give here the concrete definition of the graph parameters.

@@

\section{Results of early experiment} \label{sec:results}

Here I took ten datasets from TUDataset as examples. The calculated parameters are shown in Table~\ref{tab:parameter}. The generalization error of the models are shown in Table~\ref{tab:error}.

\begin{table}[h!]
    \centering
    \begin{tabular}{@{}lll@{}}
    \toprule
    \multicolumn{1}{c}{\multirow{2}{*}{Dataset}} & \multicolumn{2}{c}{Parameter}                                            \\ \cmidrule(l){2-3} 
    \multicolumn{1}{c}{}                         & \multicolumn{1}{c}{Ave. degree} & \multicolumn{1}{c}{Ave. shortest path} \\ \midrule
    Mutagenicity                                 & 2.0379         & 4.4825                     \\
    NCI1                                         & 2.1550         & 5.4697                     \\
    COIL-RAG                                     & 1.8277         & 1.0606                     \\
    Letter-high                                  & 1.8896         & 1.5173                     \\
    DD                                           & 4.9790         & 7.9700                     \\
    PROTEIN\_full                                & 3.7346         & 4.7123                     \\
    COLORS-3                                     & 2.9288         & 2.0945                     \\

    AIDS  &  2.01286  & 3.2864 \\
    ENZYMES  &  3.8626  & 4.4461 \\
    Cuneiform  &  4.0795  & 2.24442 \\ \bottomrule

    \end{tabular}
    \caption{The calculated parameters from a set of datasets, here used two parameters, the average degree of the graph and the average shortest path of the graph which defined in the section \ref{sec:graph_parameters}.}
    \label{tab:parameter}
\end{table}

\begin{table}[h!]
    \centering
    \begin{tabular}{@{}lll@{}}
    \toprule
    Dataset        & Ave. generalization error & Standard Deviation   \\ \midrule
    Mutagenicity   & 0.0268      & 0.02335 \\
    NCI1           & 0.0138      & 0.02649 \\
    COIL-RAG       & 0.0450      & 0.01378 \\
    Letter-high    & 0.0403      & 0.04342 \\
    DD             & 0.0524      & 0.05849 \\
    PROTEINS\_full & 0.0189      & 0.05032 \\
    COLORS-3       & 0.0076      & 0.01428 \\
    AIDS           &  0.00931    & 0.008642 \\
    ENZYMES           &  0.0345    & 0.052339 \\
    Cuneiform           &  0.2392    & 0.09868 \\ \bottomrule
    \end{tabular}
    \caption{The table shows the calculated generalization error from a set of datasets, where the generalization error is calculated as the difference between the training accuracy and the test accuracy.}
    \label{tab:error}
\end{table}

Also, I used a scatter plot to visualize the generalization error against the two graph parameters. The result is shown in Figure~\ref{fig:scatter}. Also, I calculated the correlation between the generalization error and the graph parameters. The result is shown in Table~\ref{tab:correlation}.

\begin{figure}[h!]
    \includegraphics[width=\textwidth]{final_results.png}
    \caption{The generalization error against the graph parameters, the x-axis is the average degree of the graph, the y-axis is the generalization error of the model. Each point in the plot is the calculated result from different datasets (see the table~\ref{tab:parameter}). It is obvious that more datasets are needed to get more reliable results.}
    \label{fig:scatter}
\end{figure}

\begin{table}[ht]
    \centering
    \begin{tabular}{@{}ll@{}}
    \toprule
                       & Ave. Generalization Error \\ \midrule
    Ave degree            & 0.4068                    \\
    Ave. shortest path & -0.2074                   \\ \bottomrule
    \end{tabular}
    \caption{The correlation between the generalization error and the graph parameters. The correlation is calculated by the Pearson correlation coefficient.}
    \label{tab:correlation}
    \end{table}

@@

\section{Objective of the thesis}

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.5\textwidth]{experiment_procedure.pdf}
    \caption{An illustration of experiment Procedure}
    \label{fig:experiment}
\end{figure}

>>>>

\title{\textbf{Bachelor thesis}\\
Exploration of the influence of graph parameters on the generalization error of Graph Neural Networks}

@@

\section{Introduction}\label{sec:intro}
Graph learning became a hot topic in the field of machine learning in recent years. Graph Neural Networks (GNNs), also known as deep learning on graphs, are a class of neural networks that can operate on graph-structured data, such as social networks~\cite{easley2010networks}, biological networks~\cite{barabasi2004network}, and images~\cite{simonovsky2017dynamic}. GNNs use the structure of a graph to perform "message passing", allowing information to propagate across nodes and edges. The key idea is to iteratively aggregate and update node features by exchanging information with local neighboring nodes, which allows GNNs to capture the structural information of the graph. This information is then used to make predictions. GNNs have been demonstrated to be effective in a wide range of tasks, such as node classification~\cite{hamilton2017inductive}, edge prediction~\cite{morselli2021network}, and graph classification~\cite{gilmer2017neural}. Popular GNNs in recent years include Graph Convolutional Networks (GCN)~\cite{kipf2016semi}, Graph Attention Networks (GAT)~\cite{velickovic2020pointer}, and Message Passing Neural Networks (MPNN)~\cite{gilmer2017neural}.

@@

Speaking more specifically.
First, I calculate the graph parameters for a set of datasets: Each graph has its own unique properties, such as the average degree. In graph theory, \textit{graph parameter} is used to quantify them. And a dataset consists of multiple graphs, each with its graph parameter. In the case, I calculate the average value of our desired graph parameters over all graphs in the dataset. In this thesis, 57 datasets from the TUDataset~\cite{morris2020tudataset} is used for the calculation. Second, I train different GNN models on each dataset and find that their generalization abilities varied. I show that there is a certain relationship between generalization ability and different graph parameters.

\subsection{Related work}
The following section provides an overview of the related work.

\subsubsection{Graph parameters}

\subsubsection{Generalization error}

\section{Background on learning on graphs}
The following sections provide an overview of the concepts and methods related to graph learning, machine learning, and graph neural networks.

\subsection{Notion}
At first, we need to define some terms with regard to the graph. In graph theory, we assume that $G=(V,E)$ is an undirected graph, where $V$ is the set of nodes and $E  \subseteq \{\{v,w\}\mid v,w \in V , v \neq w\}$ is the set of edges. We use $\mathbb{G}$ to represent the set of all possible graphs. The neighborhood of a node $v$ is denoted as $N(v)$, defined as $N(v) = \{w \mid \{v,w\} \in E\}$. The degree of a node $v$, denoted as $d(v)$, is the number of neighbors of $v$, that is, $d(v) = |N(v)|$. In addition to the nodes and edges that comprise the graph, we can attach a more complex set of data to each node.  A feature vector $x_n\in \mathbb{R}^k$, is attached to a node $v_n$, and in some cases, edge feature vectors are also included. These vectors can be used to characterize graphs or nodes in graphs. The adjacency matrix $A \in \mathbb{R}^{|V| \times |V|}$ is a matrix that represents the connections between nodes in the graph. The element $a_{ij}$ of the adjacency matrix is 1 if there is an edge between node $v_i$ and node $v_j$, and 0 otherwise.

\subsection{Machine learning}
Machine learning is a subfield of artificial intelligence that focuses on the development of algorithms that can learn from and make predictions or decisions based on data. The goal of machine learning is to develop models that can generalize well to unseen data. The model is trained on a training dataset, which consists of input-output pairs. The model is then evaluated on a test dataset, which is separate from the training dataset.

\subsubsection{Generalization}
A key concept in evaluating model performance or generalization ability in such task is the empirical generalization error $E_{gen}$. This is a measure of how well the model generalizes to unseen data, which can be calculated as the difference between the training accuracy and the test accuracy. It is defined as

@@

The empirical generalization error is also known as the generalization gap~\cite{goodfellow2016deep}. Typically, the learning on the training dataset and test dataset behaves differently. The model may perform well on the training dataset but poorly on the test dataset. By observing the generalization error, we can decide on a stopping criterion for the training process. And the generalization error can be used to determine whether the model is overfitting or underfitting. Furthermore, the generalization error can be influenced by many factors, such as the model architecture, the hyperparameters, and the data properties in the dataset (e.g. Graph parameter).

\subsection{Graph Neural Networks}
Graph Neural Networks (GNNs) are a class of neural networks that can operate on graph-structured data. GNNs use the structure of a graph to perform "message passing", allowing information to propagate across nodes and edges. The key idea is to iteratively aggregate and update node features by exchanging information with local neighboring nodes, which allows GNNs to capture the structural information of the graph. This information is then used to make predictions. GNNs have been demonstrated to be effective in a wide range of tasks, such as node classification, edge prediction, and graph classification. Popular GNNs in recent years include Graph Convolutional Networks (GCN), Graph Attention Networks (GAT), and Message Passing Neural Networks (MPNN).

\subsection{Graph parameters}
Now we can introduce the concept of a graph parameter. A graph parameter is a function $f: \mathbb{G} \rightarrow \mathbb{R}^d$ for $d\in \mathbb{N} >0$, which maps a graph to a d-dimensional vector over the reals. Furthermore, such functions need to be permutation invariant, i.e., $f(G) = f(\pi(G))$ for any permutation $\pi$ of the nodes of $G$, where a permutation is a function $\pi: V \rightarrow V$ and $\pi(G)$ denotes the graph obtained by permuting the nodes of $G$ according to $\pi$. A graph parameter allows us to quantify certain properties of a graph, from the basic structural numbers (number of nodes, number of edges, average degree, etc.) to distance properties (average shortest path length, diameter, etc.) to more complex properties (graph clustering coefficient, average number of coloring in the 1-WL algorithm, etc.). This thesis will focus on seven graph parameters, with definitions provided in section~\ref{sec:graph_parameters}.

\section{Experimental study}

\subsection{Experimental setup}
The following section outlines the planned methods and materials to be employed in the experiment, including the training framework, the datasets, the models, and the graph parameters.

\subsubsection{Training Framework}
The training framework is based on PyTorch Geometric~\cite{fey2019fast}. PyTorch Geometric is a library for deep learning on graphs and other irregular structures. It consists of various methods and utilities to ease the implementation of GNNs.

\subsubsection{Hyperparameters tuning}
Before training the models, for each pair of dataset and model, the hyperparameters of the model are tuned. In the experiment, 5-fold cross-validation is used to tune the hyperparameters instead of 10-fold cross validation in the final experiment. The reason is that the 10-fold cross-validation is computationally expensive and time-consuming.

The hyperparameters include the learning rate, batch size, hidden dimension, number of epochs, patience in early stopping, number of hidden layers, type of normalization, and patience of plateau scheduler. Additionally, for the GATv2 model, the number of heads, the dropout rate, and residual are also tuned.

The hyperparameters are tuned using the Bayesian optimization method\cite{frazier2018tutorial}. The hyperparameters that result in the highest validation accuracy are selected as the optimal hyperparameters for the model.

There are five models and 57 datasets, resulting in 285 pairs of dataset and model. For each pair, the hyperparameters are tuned using the Bayesian optimization method. The hyperparameters are tuned using the validation dataset. The validation dataset is a subset of the training dataset that is used to tune the hyperparameters of the model. The hyperparameters that result in the highest validation accuracy are selected as the optimal hyperparameters for the model.

\subsubsection{Datasets}
The dataset used for the classification is TUDataset~\cite{morris2020tudataset}. TUDataset is often used for the GNN evaluation. It consists of data from different domains, including small molecules, bioinformatics, social networks and synthetic. Since the size of some datasets is quite small (less than 500 data points/graphs), I use 10-fold cross validation in the training process, in order to fully utilize the data. A dataset is split into 1:1:8, where one of the folds is treated as the test dataset and another is treated as the validation dataset. The remaining folds are used for training. The training is repeated 10 times, each time with a different test fold. The average of the generalization error over the 10 runs is calculated as the final generalization error of the model.

I list information about the 57 datasets used in the experiment in the appendix~\ref{sec:datasets}.

\subsubsection{Models}
In the experiment, I plan to use different GNN layers in the model, including Graph Convolutional Networks(GCN)~\cite{kipf2016semi}, Graph Attention Networks(GAT)~\cite{velickovic2020pointer}, Graph Attention Networks(GATv2)~\cite{brody2021attentive}, Simplified Graph Convolution(SGC)~\cite{wu2019simplifying}, and Message Passing Neural Networks(MPNN)~\cite{gilmer2017neural}. The GCN model is shown in the appendix. The GCN model consists of four GCN layers, each followed by a ReLU activation function. The output of the last GCN layer is passed through a global mean pooling layer, followed by two fully connected layers.

\subsubsection{Experimental details}
The Adam optimizer~\cite{kingma2014adam} is considered to be employed in the model. To prevent overfitting and to optimize the use of time, the early stopping is employed. The loss function is defined as the cross-entropy loss function. The hyperparameters of the model are considered to be tuned. The hyperparameters include the learning rate, batch size, hidden dimension, number of epochs, and patience in early stopping. The generalization error is calculated as the difference between the training accuracy and the test accuracy.

\subsubsection{Graph Parameters Under Investigation} \label{sec:graph_parameters}
As graph parameters defined abstractly in the section~\ref{sec:intro}, I give here the concrete definition of the graph parameters.

@@

\subsection{Results}

\subsubsection{Graph parameters of the datasets}

\begin{table}[!ht]
    \footnotesize
    \centering
    \begin{tabular}{|l|l|l|l|l|l|l|l|l|l|}
    \hline
        \textbf{Name} & \textbf{Ave. degree} & \textbf{Ave. shortest path} & \textbf{Graph diameter} & \textbf{Graph density} & \textbf{Graph clustering coefficient} & \textbf{Ave. closeness centrality} & \textbf{Ave. betweenness centrality} & \textbf{Ave. eigenvector centrality} & \textbf{1-WL color count} \\ \hline
        COIL-DEL & 4.673071633424515 & 2.128750184714701 & 4.06974358974359 & 0.3275202823564923 & 0.546258039207784 & 0.5122126871677409 & 0.0647750716657882 & 0.2431245565997526 & 21.102564102564106 \\ \hline
        COIL-RAG & 1.8277218368573067 & 1.0604823111763986 & 1.242159383033419 & 0.924030303030303 & 0.5903545713545713 & 0.94372526076617 & 0.0462785547785547 & 0.5905014648511226 & 1.3115384615384615 \\ \hline
        Cuneiform & 4.079588014981273 & 2.244427103288844 & 3.0 & 0.2222330604444725 & 0.8634154547075895 & 0.4613474974345972 & 0.0722909733763576 & 0.1963017855703223 & 2.0 \\ \hline
        Fingerprint & 1.4868577990824814 & 2.115136284036567 & 4.344413012729844 & 0.4391785351497472 & 0.0017307791737759 & 0.5069423734352098 & 0.1840341453794884 & 0.4207756269406634 & 3.656584457887389 \\ \hline
        FIRSTMM\_DB & 4.50236815941043 & 12.309044701937715 & 30.676056338028168 & 0.0074027477877271 & 0.2631922211539924 & 0.0551742654129266 & 0.0188189276256195 & 0.0092704028700914 & 1357.8292682926829 \\ \hline
        Letter-high & 1.889683607525296 & 1.4794456563750826 & 2.444490301279405 & 0.5791851851851852 & 0.2976163139329805 & 0.6794971082752952 & 0.1657867724867724 & 0.4611670600331147 & 2.994222222222222 \\ \hline
        Letter-low & 1.3213534599145254 & 1.33364428641149 & 1.955783308931186 & 0.4165470899470899 & 0.0 & 0.4955472438922087 & 0.1618904761904762 & 0.4407481624189365 & 2.471111111111111 \\ \hline
        Letter-med & 1.352705840084288 & 1.3502031822344325 & 2.006610576923077 & 0.4245777777777778 & 0.0139393298059964 & 0.5071406868429822 & 0.1683222222222222 & 0.4416562761104123 & 2.517333333333333 \\ \hline
        MSRC\_9 & 4.81534002269555 & 3.113629895894764 & 7.004524886877828 & 0.1235873024311543 & 0.5412981657910688 & 0.33102605797573 & 0.055215313789426 & 0.1368862401087341 & 40.36199095022624 \\ \hline
        MSRC\_21 & 5.102391318360188 & 4.094474312024695 & 9.621669626998225 & 0.0680571076593652 & 0.5146660459581984 & 0.251511488615992 & 0.041532868642658 & 0.0936632954729105 & 77.22735346358792 \\ \hline
        MSRC\_21C & 4.782574662751558 & 3.113761314016 & 6.971291866028708 & 0.1240107738760322 & 0.5427170070575877 & 0.3315153420789583 & 0.0557392711060186 & 0.1371850938080253 & 40.05263157894737 \\ \hline
        DD & 4.979061666490266 & 7.919898418826995 & 19.70016611295681 & 0.0278322962071925 & 0.4793770769559906 & 0.1402074694227141 & 0.0324963430907113 & 0.0342447661028087 & 278.28013582342953 \\ \hline
        ENZYMES & 3.862625308732192 & 4.2810541955964485 & 10.4265625 & 0.1598878125179543 & 0.4533912862690096 & 0.263573448964092 & 0.1158938852730127 & 0.1471447702872793 & 28.575 \\ \hline
        KKI & 3.1856769969664422 & 3.500870554422239 & 8.144578313253012 & 0.1792960793494088 & 0.3526436673677589 & 0.3358793648012939 & 0.1297799757896069 & 0.1757034314039908 & 24.81927710843373 \\ \hline
        OHSU & 4.327667933476122 & 4.921680537597515 & 12.69620253164557 & 0.0822944467200859 & 0.3808295357080805 & 0.2407028072344937 & 0.0655860979728088 & 0.0823969445758651 & 77.51898734177215 \\ \hline
        Peking\_1 & 3.5514470044304343 & 3.968106920104182 & 9.623529411764704 & 0.1276151076564966 & 0.3673053988324483 & 0.2889094228756093 & 0.0998385744518594 & 0.1284748145692827 & 36.72941176470588 \\ \hline
        PROTEINS & 3.734642166440163 & 4.602185787956082 & 11.297071129707112 & 0.2121756091042708 & 0.5141966922501331 & 0.3022857727840693 & 0.118375456251276 & 0.1695057643632408 & 34.46900269541779 \\ \hline
        PROTEINS\_full & 3.734642166440163 & 4.602185787956082 & 11.297071129707112 & 0.2121756091042708 & 0.5141966922501331 & 0.3022857727840693 & 0.118375456251276 & 0.1695057643632408 & 34.46900269541779 \\ \hline
        COLORS-3 & 2.928853359699249 & 2.5810313856214724 & 5.275766205587198 & 0.1695881211511339 & 0.1450387037596311 & 0.3502761440955542 & 0.0639043708084029 & 0.1737080119571242 & 56.95904761904762 \\ \hline
        SYNTHETIC & 3.920000076293945 & 3.5064646464646465 & 7.0 & 0.0395959595959595 & 0.0203095238095238 & 0.2893391429701345 & 0.0255761698618841 & 0.0831547830080052 & 100.0 \\ \hline
        SYNTHETICnew & 3.9250000715255737 & 3.4872567329242026 & 7.274834437086093 & 0.0396464646464646 & 0.0229497089947089 & 0.289441726009901 & 0.0255427746856318 & 0.0836273264155355 & 99.96333333333334 \\ \hline
        Synthie & 3.6210444450378416 & 2.6348743925562266 & 5.494845360824742 & 0.038420429009193 & 0.0937036201778145 & 0.2766177855177352 & 0.0231922369186012 & 0.0786632559723412 & 90.6125 \\ \hline
        TRIANGLES & 3.1404920884927114 & 2.263375484124684 & 4.557498816896771 & 0.2416135135324899 & 0.2286352011335792 & 0.4374025890339534 & 0.0821216496736849 & 0.226180376713217 & 19.88371111111111 \\ \hline
        AIDS & 2.0128653862178325 & 3.490507728804514 & 7.762604013705335 & 0.1935408261794486 & 0.0071746166779525 & 0.3500774185559109 & 0.1911961844012523 & 0.262770387548969 & 11.8145 \\ \hline
        BZR & 2.1466610419897387 & 5.154837461860052 & 11.65679012345679 & 0.0648920405178712 & 8.903397114779228e-05 & 0.2054846442932875 & 0.1245291263310628 & 0.1416530437212679 & 29.607407407407408 \\ \hline
        BZR\_MD & 20.30392156862745 & 1.0 & 1.0 & 1.0 & 1.0 & 1.0 & 0.0 & 0.2203726689661978 & 1.0 \\ \hline
        COX2 & 2.107735009469108 & 5.936420803578038 & 13.790149892933618 & 0.0529052472359257 & 0.0007216110850642 & 0.1757209022905502 & 0.1262987138392391 & 0.1288265342157682 & 28.09421841541756 \\ \hline
        COX2\_MD & 25.27722772277228 & 1.0 & 1.0 & 1.0 & 1.0 & 1.0 & 0.0 & 0.1957034193657646 & 1.0 \\ \hline
        DHFR & 2.102359890622437 & 6.144674814243727 & 14.603174603174605 & 0.0536754666970741 & 0.0 & 0.1734264353163348 & 0.1288500765571343 & 0.1271607693927877 & 32.21560846560847 \\ \hline
        DHFR\_MD & 22.8676844783715 & 1.0 & 1.0 & 1.0 & 1.0 & 1.0 & 0.0 & 0.2076620678810238 & 1.0 \\ \hline
        ER\_MD & 20.327354260089685 & 1.0 & 1.0 & 1.0 & 1.0 & 1.0 & 0.0 & 0.2244695039966339 & 1.0 \\ \hline
        FRANKENSTEIN & 2.0627741588132293 & 3.6742676066855062 & 8.423452029938762 & 0.1705038719060743 & 0.0106826329262756 & 0.3148146889108825 & 0.1923606317376928 & 0.2432099454364741 & 13.42448697256168 \\ \hline
        MCF-7 & 2.1516180606917765 & 5.050070569624072 & 12.141178938535766 & 0.0980572307942984 & 0.0020345164969653 & 0.2175444791564102 & 0.1724077067751488 & 0.1725022149133201 & 21.418113071660063 \\ \hline
        MCF-7H & 2.0888838372172147 & 5.858613378052236 & 13.306228605946709 & 0.0537227676449342 & 0.0005825022974507 & 0.1778419519669024 & 0.1198217621207925 & 0.1223362659022958 & 32.9756211739287 \\ \hline
        MOLT-4 & 2.146077948348501 & 4.951738679286625 & 11.874633536790505 & 0.0987082247303717 & 0.0019246147011501 & 0.2183304220273518 & 0.1714407445609207 & 0.1734293274657891 & 21.028995347667543 \\ \hline
        MOLT-4H & 2.0858484049375803 & 5.738056140581633 & 12.992424764134702 & 0.0539489355320176 & 0.0005343843281943 & 0.17815930623996 & 0.1192636780853368 & 0.1228930198480923 & 32.272249465610464 \\ \hline
        Mutagenicity & 2.0379886209469995 & 4.418912992995495 & 9.63701923076923 & 0.0912875415379717 & 0.0031125822886973 & 0.2466634939984061 & 0.1371754284356414 & 0.1710356482094367 & 20.874567673507038 \\ \hline
        MUTAG & 2.18877208359698 & 3.626150957182829 & 8.21808510638298 & 0.1384540671648269 & 0.0 & 0.293764054092514 & 0.1694459751944365 & 0.2197353385133972 & 14.8031914893617 \\ \hline
        NCI1 & 2.15501380214726 & 5.234873158476093 & 12.659402381487306 & 0.088944910671084 & 0.0030999008340164 & 0.2026186665583615 & 0.1631676786426253 & 0.1607325923179734 & 24.721411192214116 \\ \hline
        NCI109 & 2.156446177386937 & 5.183950502801717 & 12.49528936742934 & 0.0894286690245151 & 0.0030732389355228 & 0.20411132911515 & 0.1624231134845694 & 0.1617585552708976 & 24.52410952265568 \\ \hline
        NCI-H23 & 2.1451602406810686 & 4.950946501654924 & 11.869525050337558 & 0.0987776628128759 & 0.0018996992922189 & 0.2183535143438838 & 0.1715792456717554 & 0.1735208031755432 & 20.99303645329963 \\ \hline
        NCI-H23H & 2.085327596320919 & 5.734343001278942 & 12.983736711151325 & 0.0539842770435475 & 0.0005268942359655 & 0.1782099752168056 & 0.1192891041739607 & 0.1229635264798962 & 32.22578246970485 \\ \hline
        OVCAR-8 & 2.145637268375766 & 4.945169149304127 & 11.85222800857742 & 0.0987730040211328 & 0.0018986224960467 & 0.2183941696064956 & 0.171403631603811 & 0.1735393405097124 & 20.98556125974924 \\ \hline
        OVCAR-8H & 2.0856259705836995 & 5.728655397369023 & 12.966769410758882 & 0.0539777071171825 & 0.0005298176630677 & 0.1782129665549435 & 0.1192148511162624 & 0.1229665170804826 & 32.22561457202093 \\ \hline
        P388 & 2.109217112454913 & 4.355752638151867 & 10.21824835544779 & 0.1190787859581164 & 0.0037544697177687 & 0.2459957278657192 & 0.1789538865626834 & 0.1958220277248745 & 17.133174189814813 \\ \hline
        P388H & 2.0638945394922854 & 5.289795718220624 & 11.765664188214403 & 0.0639638393366292 & 0.0009642194122106 & 0.1971310478874152 & 0.1240122910178544 & 0.1373237905541068 & 26.71100983796296 \\ \hline
        PC-3 & 2.1520653447146643 & 5.05018085139685 & 12.140862989009436 & 0.098055200309084 & 0.0019733135754618 & 0.2175815805232795 & 0.1725492873407526 & 0.172560720893664 & 21.37340506743248 \\ \hline
        PC-3H & 2.08922384690422 & 5.857822430952191 & 13.30650249313117 & 0.0537656750613318 & 0.0005561305149752 & 0.1779189564869681 & 0.1200247359820712 & 0.1224665687629844 & 32.881929550328984 \\ \hline
        PTC\_FM & 1.9758043374578045 & 3.311647990381311 & 7.36676217765043 & 0.2154944740700171 & 0.0091220986824968 & 0.3693003427913903 & 0.2055882581121011 & 0.2786143302706905 & 9.91404011461318 \\ \hline
        PTC\_FR & 1.9863111707899304 & 3.387662268892836 & 7.589743589743589 & 0.2085568638656639 & 0.0088214579442649 & 0.3612672957602951 & 0.2045358868174996 & 0.2734008790739162 & 10.22222222222222 \\ \hline
        PTC\_MM & 1.9701179610121815 & 3.301432053360394 & 7.339285714285714 & 0.2223452925857377 & 0.0130582137161084 & 0.374488207420213 & 0.2059637189235834 & 0.2823441282735879 & 9.803571428571429 \\ \hline
        PTC\_MR & 1.9805375618297 & 3.3577641223936463 & 7.523255813953488 & 0.2137888896192228 & 0.009509685286154 & 0.3666473296924281 & 0.2062170509277356 & 0.2777684525909222 & 10.040697674418604 \\ \hline
        SF-295 & 2.145489384462884 & 4.9445677038396125 & 11.852116182572614 & 0.09881526807439 & 0.0019131887956769 & 0.2184346701016761 & 0.1714761059761314 & 0.1735919743359789 & 20.97159246107621 \\ \hline
        SF-295H & 2.0855234748235936 & 5.727434951743517 & 12.9664274556856 & 0.0539895579758234 & 0.0005299113307649 & 0.1782697110808576 & 0.1192036786794211 & 0.1229816733300816 & 32.196146110104046 \\ \hline
        SN12C & 2.145026913904858 & 4.94825141099449 & 11.86401279205747 & 0.0987936439503507 & 0.001927945706436 & 0.2183468315283276 & 0.1714975830848956 & 0.1735570013676089 & 20.99167583241676 \\ \hline
        SN12CH & 2.0853053252079072 & 5.730086714838555 & 12.973598487437071 & 0.0540104189866913 & 0.0005390487212868 & 0.1781938757210136 & 0.1192686561921279 & 0.1230077396296653 & 32.236301369863014 \\ \hline
        SW-620 & 2.1452310279340394 & 4.94393636762053 & 11.851577038136291 & 0.0988746005232462 & 0.0018522578567537 & 0.2185003794708548 & 0.1714920826604129 & 0.1736489333480562 & 20.97197276226192 \\ \hline
        SW-620H & 2.0854275176564645 & 5.725806234940699 & 12.962851360467733 & 0.054054544610838 & 0.0005110193017508 & 0.1783225632271403 & 0.1192839052512742 & 0.1230820111720522 & 32.19651139840126 \\ \hline
        UACC257 & 2.145698715720169 & 4.955834964420495 & 11.885704040162564 & 0.0987250195703296 & 0.0018738116805416 & 0.218300263582104 & 0.1716221375949755 & 0.1734631006815176 & 20.994198259477844 \\ \hline
        UACC257H & 2.0856917230912635 & 5.740515645090362 & 13.003174313183676 & 0.0539749990285044 & 0.0005209407683445 & 0.1781806662974605 & 0.1193640515072574 & 0.122956068725157 & 32.22436731019306 \\ \hline
        Yeast & 2.099442849357738 & 4.364322361013096 & 10.26343257027636 & 0.1210553127513687 & 0.0022671334945899 & 0.2476806589296417 & 0.183060827627568 & 0.1985665767951158 & 16.67475282973832 \\ \hline
        YeastH & 2.0589509621359707 & 5.245391698622407 & 11.6875493153864 & 0.0642704732457107 & 0.0005773570062507 & 0.1983872537891083 & 0.1254655281986756 & 0.1384817929367545 & 26.05320284921044 \\ \hline
        Sum & 242.8347529362711 & 258.6723790469145 & 587.9183294923151 & 12.731666924394474 & 11.845921907393928 & 20.687237238791475 & 7.3848149134808 & 11.636469235194477 & 3245.599253687252 \\ \hline
    \end{tabular}
    \caption{Graph parameters of the datasets}
\end{table}

@@

\subsubsection{Generalization error of GCN model}
